\recette{Spaghetti Carbonara}
\preptime{10 min} \cooktime{15 mins} \people{4}

\vspace{-10mm}
\recipe{
    \unit[1]tbsp     & Olive Oil \\
    \unit[300]{g}    & Bacon, cut in small pieces \\
    \unit[2]{cloves} & Garlic, bashed \\
    \unit[400]{g}    & Spaghetti \\
    4                & Egg yokes \\
    \unit[100]{g}    & Parmesan, finely grated \\
}{
  \item Warm serving dishes in a low oven or microwave.

  \item Fry the bacon and garlic in oil for 10
    mins, or until the bacon is crisp. Remove and
    discard the garlic cloves. Turn off the heat.
    
  \item  Bring a large pan of salted water to simmer and cook the pasta until it is
    al dente (about a minute less than the pack instructions).
    Meanwhile, whisk egg yokes with a pinch of salt.

  \item Using tongs, lift the pasta into the bacon pan. Keep the pasta water. If
    the pan looks dry, add a spoonful of pasta water, and mix in. Keep adding
    until you see a little bit of pasta water left in the pan.

  \item Working quickly, tip the beaten egg yokes into the pasta and stir
    vigorously. Rinse out the yoke bowl with a little bit more pasta water. Add
    most of the cheese and mix again.
    \textit{(If at any time the sauce becomes claggy or is starting to scramble, pour in
    a little more water. If you add too much, stir the pasta over low heat for a
    few moments. You are aiming for a smooth sauce that has the consistency of
    double cream, Season with black pepper and salt to taste.)}
    
\item Transfer pasta to the warmed serving dishes, scatter over the remaining
  cheese.
}

Suggested changes: Instead of Bacon, use Rindless, unsmoked fatty pancetta or guanciale;
Instead of Parmesan, use Finely grated cheddar cheese. 

\textbf{Hint:} The egg whites can be used in the Meringue recipe for dessert.


