\recette{Medoviv - Honey Cake Base}
\preptime{20 min} \baketime{20 min 180\textdegree C/350 \textdegree F, 4-5 min per tray} \UKR

\vspace{-10mm}
\recipe{
    \unit[4]{tbsp}  & (1/4 cup)  Honey \\
    \unit[3/4]{cup} & Granulated sugar \\
    \unit[2]{tbsp}  & Unsalted butter \\
    3               & Large eggs, room temperature, beaten with a fork \\
    \unit[1]{tsp}   & Baking soda \\
    \unit[3]{cup}   & All-purpose flour \\
}{
    \item Add sugar, honey and butter to a medium sauce pan and melt them together over medium/low heat,
    whisking occasionally until sugar is melted (5-7 mins).
    
    \item As soon as the sugar is dissolved, remove from heat and while it’s still hot, 
    add in your beaten eggs in a slow steady stream while whisking vigorously until
    all of your eggs are incorporated (whisk constantly so you don’t end up with scrambled eggs).

    \item Whisk in the baking soda until no lumps remain, then fold in flour 1/2 cup at a time
    with a spatula until the dough reaches a clay consistency and doesn’t stick to your hands.

    \item Cut the dough into 8 equal pieces. On a well-floured surface, roll each piece out into
    a thin 9'' circle (about 1/8'' thick). Use a plate (or springform base) over your
    rolled dough to cut a circle. Keep the scraps for later.
    Transfer the dough to a large sheet of parchment paper and bake 2 at a time 
    for 4-5 minutes or until golden. 
    Transfer to a wire rack and let cool completely before stacking. Repeat with remaining layers

    \item Finally, bake the scraps.
    Once baked, cooled and firm, you can crush them with a rolling pin
    or pulse them in a food processor until you have fine crumbs.
}
